Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-20 doc/mc-paper.tex
Fix capitalization

\section{Clausal Proof Frameworks}

@@

\subsection{Forward implication proof}

@@

\subsection{Reverse implication proof}

@@

We found that the monolithic approach for generating the forward
implication proof works well for smaller POGs, but it becomes
unreliable and inefficient for larger ones.  These experiments suggest
a possible hybrid approach, stopping the recursion of the structural
approach and shifting to monolithic mode once the subgraph size is below some
threshold.  We found that our two optimizations: literal grouping and
lemmas can provide substantial improvements in proof size and runtime.

Running the verified proof checker in \lean{} showed the same scaling
with respect to the proof size as did the prototype checker, but it
required, on average, around 5.9 times longer.

@@

\input{figure-runtime-d4-verify}

@@

\input{figure-clauses-d4-verify}

@@

\input{figure-runtime-monolithic}

\input{figure-clauses-monolithic}

@@

@@

\subsection{Comparison with MICE Framework}

>>>>

\section{Clausal Proof Framework}

@@

@@

@@

We found that the monolithic approach for generating the forward
implication proof works well for smaller POGs, but it becomes
unreliable and inefficient for larger ones.
%% These experiments suggest
%% a possible hybrid approach, stopping the recursion of the structural
%% approach and shifting to monolithic mode once the subgraph size is below some
%% threshold.
We also found that our two optimizations: literal grouping and
lemmas can provide substantial improvements in proof size and runtime.
Running the verified proof checker in \lean{} showed the same scaling
with respect to the proof size as did the prototype checker, but it
required, on average, around 5.9 times longer.

@@

\input{figure-runtime-d4-verify}
\input{figure-clauses-d4-verify}

@@

@@

@@

\input{figure-runtime-monolithic}
\input{figure-clauses-monolithic}

@@

\subsection{Comparison with the MICE Framework}
